Data Appendix to \"The impact of weather events on schooling outcomes\

### 2020-04-24 data_appendix_all_years.Rmd
commit

```{r regression variable specifications}
total_subset %>%
  mutate(ln_income = log(income))
reg_data <- total_subset %>%
  mutate(year_factor = as.factor(year))

>>>>

```{r regression variable specifications}
total_subset %>%
  mutate(ln_income = log(income),
         literate = literacy-1,
         female = sex-1,
         no_assist = assist-1,
         not_registered = register-1)
#trying to make the assist, register, sex, and literacy variables into 0 1 binary variables, with assist and register = 1, sex = 1 if female, and literacy = 1 if literate. The current coding from the original data is all in 1 2 format, with the opposites. Trying to change it by subtracting doesn't seem to be working.
reg_data <- total_subset %>%
  mutate(year_factor = as.factor(year))
